
\documentclass{article}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\section*{Difference-in-Differences (DiD) Analysis}

\subsection*{Model Specification}

We estimate the following fixed-effects DiD model with clustered standard errors at the country level:

\[
\log(\text{Average\_price}_{it}) = \beta_0 + \beta_1 \cdot \text{post}_t + \alpha_i + \lambda_t + \epsilon_{it}
\]

where
\begin{itemize}
    \item $\log(\text{Average\_price}_{it})$ is the log of the average price for country $i$ in year $t$,
    \item $\text{post}_t$ is a dummy variable indicating the post-treatment period,
    \item $\alpha_i$ are country fixed effects,
    \item $\lambda_t$ are year fixed effects,
    \item $\epsilon_{it}$ is the error term clustered at the country level.
\end{itemize}

\bigskip

\subsection*{Estimation Results}

\begin{table}[ht]
\centering
\caption{OLS Fixed-Effects Regression with Clustered Standard Errors (Cluster: Countries)}
\begin{tabular}{lcccc}
\toprule
Variable & Estimate & Std. Error & t value & $p$-value \\
\midrule
post & -0.0611 & 0.0914 & -0.669 & 0.507 \\
\bottomrule
\multicolumn{5}{l}{\footnotesize{Significance codes: *** $p<0.001$, ** $p<0.01$, * $p<0.05$, . $p<0.1$}} \\
\multicolumn{5}{l}{Observations: 1,101 \quad Countries (Fixed Effects): 45 \quad Years (Fixed Effects): 26} \\
\multicolumn{5}{l}{RMSE: 0.1514 \quad Adjusted $R^2$: 0.6156 \quad Within-$R^2$: 0.0023} \\
\end{tabular}
\label{tab:did_results}
\end{table}

\bigskip

\subsection*{Interpretation}

The estimated coefficient for the variable \texttt{post} is \(-0.0611\) and is statistically insignificant (\(p = 0.507\)). This suggests that there is no significant change in the logged average price after treatment when controlling for country and year fixed effects as well as clustered standard errors.

The model includes 1,101 observations from 45 countries over 26 years. The relatively low within-$R^2$ of 0.0023 indicates that the model explains little variation within countries over time. The adjusted overall $R^2$ of 0.6156 reflects the variation explained by all explanatory variables including fixed effects.

The results imply that the "post" effect is not robustly detectable in this setting. Further investigations could include additional control variables or alternative model specifications.

\end{document}

